---
slug: "1"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 1: `r datalegreyar::fig(datalegreyar::datafy(4 + 3 * 1:20, "datalegreyar"), size = 64)`

Welcome all to the first day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today I'm going to start simple and awesome with the [datalegreyar](https://github.com/emitanaka/datalegreyar) package by [Emi Tanaka](https://twitter.com/statsgen). 
The package provides an interface to the font [datalagreya](https://github.com/figs-lab/datalegreya) developed by [Figs](https://www.figs-lab.com/).

Since the package still is on GitHub you need to download it from there

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github('emitanaka/datalegreyar')
```

A datalegreyar composition requires two main parts. 
The text and the underlying data used to create the line. 
Where I'm living, Christmas music has been playing for quite a while, 
with "Last Christmas" being quite a popular choice. 
We can use the [gtrendsR](https://github.com/PMassicotte/gtrendsR) to retrieve the hit data from the last 3 months.
Please note that the CRAN version of **gtrendsR** isn't working well, 
download the developmental version from GitHub if you want to follow along.

```{r}
# remotes::install_github("PMassicotte/gtrendsR")
library(gtrendsR)
last_christmas <- gtrends("Last Christmas", time = "today 3-m")
```

Then we load the **datalegreyar** package and use the `datafy()` function to combine the values and the text. 
Furthermore, we also specify that we would want to ignore the spaces so we have one continuous line.

```{r}
library(datalegreyar)
last_christmas_data <- datafy(
  values = last_christmas$interest_over_time$hits,
  text = "Last Christmas",
  ignore_space = FALSE
)

last_christmas_data
```

Next, we pass the datafied object to `fig()` to render it in our document. 
I have manually set size to 60 as the default is quite small.

```{r}
fig(last_christmas_data, size = 60)
```

From here on we can add our final stylistic choice. 
There are simple self-explanatory arguments such as `color` and `bgcolor`(background color).
One of the prominent is the `type` argument which specifies the area under the curve.

```{r}
fig(last_christmas_data, size = 60, type = "thin")
fig(last_christmas_data, size = 60, type = "gradient")
fig(last_christmas_data, size = 60, type = "dot")
```

I like the gradient type so I'll stick with that one for now.
Last we will use the `xlabs` argument to add little text above the datalegreyar.
I'll use the opportunity to label the start and endpoints for dates.

```{r}
fig(last_christmas_data, size = 60, type = "gradient", 
    xlabs = c("sep 1", "dec 1"))
```

## Santa's little datalegreyar factory

I already decided on a style I like, so I'm going to wrap up everything into a function and pass in a bunch of Christmas Song titles.

```{r}
datalegreyar_factory <- function(text, size) {
  data <- datafy(
    values = gtrends(text, time = "today 3-m")$interest_over_time$hits,
    text = text,
    ignore_space = FALSE
  )
  fig(data, size = size, type = "gradient", xlabs = c("sep 1", "dec 1"))
}
```

Then we just apply it many times and see the magic! 
This is all for today, keep an eye out for the next opening tomorrow!

```{r}
datalegreyar_factory("Drummer Boy", size = 60) 
```


```{r}
datalegreyar_factory("White Christmas", size = 50) 
```


```{r}
datalegreyar_factory("We Wish You A Mary Christmas", size = 30) 
```
