---
slug: "10"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 10: reactable

```{css}
.ReactTable {
  background: #2f3238;
}
```


Welcome back for the 10th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at a new contender for table creation. 
I'm talking about the [reactable](https://github.com/glin/reactable) package created by [Greg Lin](https://github.com/glin). 
**reactable** is a wrapper around the JavaScript library [react-table](https://github.com/tannerlinsley/react-table).

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("reactable")
```

We will be using the `elf` data from [day 7](https://www.hvitfeldt.me/pkgcal2019/7/).

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
set.seed(1234)

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly"))) %>%
  mutate_if(is.numeric, jitter) %>%
  mutate_if(is.numeric, ~ round(., 2))
```

You simply pass your data.frame to the `reactable()` function and it generates a nice looking table.

```{r, message=FALSE}
library(reactable) 

reactable(elf)
```

**reactable** is highly customizable with its many arguments in `reactable()`.
Additionally, if you know JavaScript you can raise it to new heights.

There are many more things you can do with this package and I highly encourage you to visit the package [website](https://glin.github.io/reactable/).

## Additional Resources

- [Many examples](https://glin.github.io/reactable/articles/examples.html)

<details>
 <summary>Creating `elf` dataset</summary>

```{r}
library(tidyverse)
set.seed(1234)

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly"))) %>%
  mutate_if(is.numeric, jitter)
```

</details>
