---
slug: "11"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 11: slide

Welcome back for the 11th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the handy new package [slide](https://github.com/DavisVaughan/slide) by [Davis Vaughan](https://twitter.com/dvaughan32).
The main purpose of **slide** is to provide a more general-purpose approach to sliding window functions.

The package is not yet available from CRAN but can be downloaded with

```{r, eval=FALSE}
remotes::install_github("DavisVaughan/slide")
```

The package on the surface looks a lot like [purrr](https://purrr.tidyverse.org/).
You have 3 main functions `slide()`, `slide_index()` and `slide_between()`,
who all have `**_dbl()`, `**2()` and `p**()` variants.

For the examples, we will use the data we also used for [day 1](https://www.hvitfeldt.me/pkgcal2019/1/).

```{r}
# remotes::install_github("PMassicotte/gtrendsR")
library(gtrendsR)
library(skimr)
last_christmas <- gtrends("Last Christmas", time = "today 3-m")$interest_over_time

skim(last_christmas)
```

Lets try to plot the `hits` variable over time (`date`) using [ggplot2](https://ggplot2.tidyverse.org/).

```{r}
library(ggplot2)
ggplot(last_christmas, aes(date, hits)) +
  geom_point()
```

suppose we want to apply a rolling average to the hits variable.
For this we will use the `slide()` function, you pass the object you want to iterate over and what to do it.
Similar style to how we do it in **purrr**, notice how I specified `_dbl()` as I know the answer should be numeric.

```{r}
library(slide)
slide_dbl(last_christmas$hits, ~mean(.x))
```

However, nothing actually happened in this example as the sliding window had length 1.
Instead let's calculate the average of the last 5 days, or I other words: today + last 4 days.
We do this by specifying `.before = 4`.

```{r}
slide_dbl(last_christmas$hits, mean, .before = 4)
```

Notice how the output has the same length as the input.
This makes it easy to use inside other functions such as `mutate()`.

Now let's calculate the moving average again and plot it on top of our plot.

```{r, message=FALSE}
library(dplyr)
last_christmas %>%
  mutate(hits_ma5 = slide_dbl(hits, ~mean(.x), .before = 4)) %>%
  ggplot(aes(date, hits)) +
  geom_point() +
  geom_line(aes(y = hits_ma5), color = "firebrick")
```

Lastly, I would like to note that you can use arbitrary functions inside your `slide()`.
Take a look at the additional resources for many more examples of what **slide** can do.

## Additional resources

- [Row-wise iteration with slide](https://davisvaughan.github.io/slide/articles/rowwise.html)
- [Moving Averages and Calendars](https://www.youtube.com/watch?v=sbrhxvpP3iw)
