---
slug: "12"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 12: polite

Welcome back for the 12th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [polite](https://github.com/dmi3kno/polite) by [Dmytro Perepolkin](https://twitter.com/dmi3k).
The **polite** package helps you be considerate when scraping the web.

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("polite")
```

The main functions for this package is `bow()` and `scrape()`.
First to call `bow()` on the website you intend to scrape.
This will set up a session with permission, set up a connection and establish settings.

```{r}
library(polite)

session <- bow("https://www.classicfm.com/discover-music/occasions/christmas/nations-top-30-christmas-carols/")
session
```

We can then use `scrape()` to the HTML object that we can investigate with [rvest](https://rvest.tidyverse.org/).

```{r}
library(rvest)
scrape(session) %>%
  html_nodes("h2") %>%
  html_text()
```

There are more examples of the package [website](https://dmi3kno.github.io/polite/) of expended examples.

## Additional resources

- [Presentation of {polite} at UseR'19 in Toulouse (11 July 2019)](https://github.com/dmi3kno/user19-polite)
