---
slug: "14"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 14: networkdata

Welcome back for the 14th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [networkdata](https://github.com/schochastics/networkdata) package by [David Schoch](https://twitter.com/schochastics).
The **networkdata** package provides over 2000 networks from almost 1000 datasets at the time of writing.

The package is not yet available from CRAN but can be downloaded with

```{r, eval=FALSE}
remotes::install_github("schochastics/networkdata")
```

The package itself is fairly straightforward. All the datasets come in `igraph` format.
All the datasets along with metadata can be seen using the `show_networks()` function

```{css, echo=FALSE}
.ReactTable {
  background: #2f3238;
}
```

```{r}
library(networkdata)
library(reactable)
reactable(show_networks())
```

the dataset `movie_751` contains the interactions of characters in the movie ["White Christmas" (1954)](https://www.imdb.com/title/tt0047673).

We can use the [ggraph](https://ggraph.data-imaginist.com/) package to plot the network

```{r, eval=FALSE}
library(ggraph)
ggraph(movie_751, layout = "circle") +
  geom_edge_link(aes(alpha = weight), color = "firebrick") +
  geom_node_label(aes(label = name)) + 
  theme(
    legend.position = "none"
  )
```

```{r, echo=FALSE}
library(ggraph)
ggraph(movie_751, layout = "circle") +
  geom_edge_link(aes(alpha = weight), color = "firebrick") +
  geom_node_label(aes(label = name)) + 
  theme(
    legend.position = "none",
    panel.background = element_rect(fill = "#2f3238"),
    plot.background = element_rect(fill = "#2f3238", color = NA)
    )
```
