---
slug: "15"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 15: covr

Welcome back for the 15th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [covr](https://github.com/r-lib/covr) package by [Jim Hester](https://twitter.com/jimhester_).
The **covr** package helps you track test coverage for your R packages.

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("covr")
```

once you start developing packages you get to a point where you start thinking about implementing [unit tests](http://r-pkgs.had.co.nz/tests.html).
**covr** helps you keep track of which parts of the code have had tests done on them.
Setting up **covr** is really easy to set up if you use the [usethis](https://usethis.r-lib.org/) package.
You simply run the following command and follow the instructions.

```{r, eval=FALSE}
usethis::use_coverage()
```

for local usage you can use the `package_coverage()` to get a printout of your coverage.
For this example, I have cheated a little bit to showcase the result for my [prismatic](https://github.com/EmilHvitfeldt/prismatic) package.

```{r, eval=FALSE}
library(covr)
package_coverage()
```

```{r, echo=FALSE}
library(covr)
package_coverage("~/Github/prismatic/")
```

The `report()` function will run `package_coverage()` in the background and will return an interactive table so you can see which lines have been tested.

That is everything I have for today, I look forward to seeing you again tomorrow!
