---
slug: "16"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 16: Sparkline

Welcome back for the 16th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [sparkline](https://github.com/htmlwidgets/sparkline) package by [Kent Russell](https://twitter.com/timelyportfolio).
The **sparkline** package provides a wrapper around the jQuery library [of the same name](https://omnipotent.net/jquery.sparkline/#s-about).

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("Sparkline")
```

This package is quite similar to the [datalegreyar](https://github.com/emitanaka/datalegreyar) package from [day 1](https://www.hvitfeldt.me/pkgcal2019/1/).

**sparkline** will take a series of numbers and create a miniature chart from them.
Here we will reuse data from [day 13](https://www.hvitfeldt.me/pkgcal2019/1/)

```{r, echo=FALSE}
carrols <- c("O Holy Night", "Silent Night", 
             "O Come All Ye Faithful")

library(gtrendsR)
carrol_trends <- gtrends(carrols)$interest_over_time
```

First, let's pull out a single time-series using [dplyr](https://dplyr.tidyverse.org/).

```{r, message=FALSE}
library(dplyr)
holy_nights_hits <- carrol_trends %>%
  filter(keyword == "O Holy Night") %>%
  mutate(hits = as.numeric(if_else(hits == "<1", "0", hits))) %>%
  pull(hits)
```

Then we simply pass the vector to the `sparkline()` function.

```{r, eval=FALSE}
library(sparkline)
sparkline(holy_nights_hits)
```

```{r, echo=FALSE}
library(sparkline)
sparkline(holy_nights_hits, width = "100%", height = 60)
```

What makes **sparkline**s really special is the ability for you to embed them in other applications.
In the following example, we group the data by keyword and year. 
Then we have a sparkline for each year inside our table.

```{css}
.ReactTable {
  background: #2f3238;
}
```

```{r}
library(reactable)
library(dplyr)
library(sparkline)
library(lubridate)

data <- carrol_trends %>%
  mutate(hits = as.numeric(if_else(hits == "<1", "0", hits)),
         year = year(date)) %>%
  filter(year > 2014) %>%
  group_by(keyword, year) %>%
  summarise(hits = list(hits))

reactable(data, columns = list(
  hits = colDef(cell = function(values) {
    sparkline(values)
  })
))
```

This is all for today. **sparkline** is highly customizable and can be used in many applications.

