---
slug: "17"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 17: golem

Welcome back for the 17th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [golem](https://github.com/ThinkR-open/golem) package by [Colin Fay](https://twitter.com/_ColinFay).
The **golem** package provides is an opinionated framework for building production-grade shiny applications.

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("golem")
```

This post is going to be quite different simply because it can be quite hard to illustrate shiny development in a short-form blog post.
I'll instead provide a bunch of links to great resources that you can go to to learn how to use **golem**. This list is very similar to the one found on the package [website](https://thinkr-open.github.io/golem/index.html).

<iframe width="100%" height="315" src="https://www.youtube.com/embed/3-p9XLvoJV0" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

- [Getting started with `golem`](https://thinkr-open.github.io/golem/articles/a_start.html)
- [Building Big Shiny Apps - A Workflow - book](https://thinkr-open.github.io/building-shiny-apps-workflow/)
- [Building Big Shiny Apps - A Workflow - blogpost](https://rtask.thinkr.fr/building-big-shiny-apps-a-workflow-1/)
