---
slug: "18"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 18: flexdashboard

Welcome back for the 18th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [flexdashboard](https://github.com/rstudio/flexdashboard).
The **flexdashboard** package helps you create interactive dashboards for R.

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("flexdashboard")
```

Today's post is going to resemble yesterday's post in the sense that there won't be much code.

**flexdashboard** gives you the power to create nice interactive dashboards.
A great first place to start learning is directly on the package [website](https://rmarkdown.rstudio.com/flexdashboard/using.html).
The page includes information regarding [layout](https://rmarkdown.rstudio.com/flexdashboard/using.html#layout), [sizing](https://rmarkdown.rstudio.com/flexdashboard/using.html#sizing), [storyboards](https://rmarkdown.rstudio.com/flexdashboard/using.html#storyboards) and much [more](https://rmarkdown.rstudio.com/flexdashboard/using.html#learning_more).

If you are looking for inspiration taking a look at the [gallary](https://rmarkdown.rstudio.com/flexdashboard/examples.html) is well worth it.
Another great resource is a [post](https://p8105.com/plotly_and_dashboards.html) by the [Fall of 2018 through the Biostatistics Department at the Columbia School of Public Health](https://p8105.com/index.html).
