---
slug: "19"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 19: ggtext

Welcome back for the 19th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [ggtext](https://github.com/clauswilke/ggtext) package by [Claus Wilke](https://twitter.com/ClausWilke).
The **ggtext** package provides improved text rendering support for [ggplot2](https://ggplot2.tidyverse.org/).

The package is not yet available from CRAN but can be downloaded with

```{r, eval=FALSE}
remotes::install_github("clauswilke/ggtext")
```

For the following example, we will use the "Last Christmas" data from earlier posts.

```{r}
# remotes::install_github("PMassicotte/gtrendsR")
library(gtrendsR)
last_christmas <- gtrends("Last Christmas", time = "today 3-m")$interest_over_time
```

And we will be building off the chart we created back in [day 11](https://www.hvitfeldt.me/pkgcal2019/11/)

```{r, message=FALSE}
library(ggplot2)
library(slide)
library(dplyr)
last_christmas %>%
  mutate(hits_ma5 = slide_dbl(hits, ~mean(.x), .before = 4)) %>%
  ggplot(aes(date, hits)) +
  geom_point() +
  geom_line(aes(y = hits_ma5), color = "firebrick")
```

**ggtext** introduces a new theme element, `element_markdown()`, which behaves similarly to `element_text()` but renders the text as markdown/HTML.
Suppose you want to selectively bold part of our title. 
Using markdown we would put the text in double stars.

```{r}
last_christmas %>%
  mutate(hits_ma5 = slide_dbl(hits, ~mean(.x), .before = 4)) %>%
  ggplot(aes(date, hits)) +
  geom_point() +
  geom_line(aes(y = hits_ma5), color = "firebrick") +
  labs(title = "I only want **this** part in bold")
```

But using normal **ggplot2** doesn't allow you to do that.
There is where **ggtext** comes in, we use the `theme()` function to specify the plot title to be rendered using markdown.

```{r, warning=FALSE}
library(ggtext)
last_christmas %>%
  mutate(hits_ma5 = slide_dbl(hits, ~mean(.x), .before = 4)) %>%
  ggplot(aes(date, hits)) +
  geom_point() +
  geom_line(aes(y = hits_ma5), color = "firebrick") +
  labs(title = "I only want **this** part in bold") +
  theme(plot.title = element_markdown())
```

Additionally, you can also use standard HTML syntax to modify your text

```{r, warning=FALSE}
last_christmas %>%
  mutate(hits_ma5 = slide_dbl(hits, ~mean(.x), .before = 4)) %>%
  ggplot(aes(date, hits)) +
  geom_point() +
  geom_line(aes(y = hits_ma5), color = "firebrick") +
  labs(title =  "<i style='color:#FF3030'>I only want **this** part in bold</i>") +
  theme(plot.title = element_markdown())
```

