---
slug: "2"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 2: glue

Welcome back for the second day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be talking about the little package called [glue](https://github.com/tidyverse/glue) package by [Jim Hester](https://twitter.com/jimhester_).

the package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("glue")
```

**glue** provides a way to do simple string interpretation using a simple syntax.
The user can pass expressions into the string to be evaluated.
This approach will feel similar to `sprintf()` expect that `glue()` shows the location in place.
Simply pass any expression into the string by wrapping it in curly brackets ({}).
`glue()` will vectorize when needed.

```{r}
library(glue)

color <- "red"
glue("Santa packed a {color} present")

color <- c("red", "blue", "green")
glue("Santa packed a {color} present")
```

This is commonly done by passing in a defined variable outside `glue()`,
but remember that any expression can be passed to `glue()`.

```{r}
glue("`mtcars` has {nrow(mtcars)} rows and {ncol(mtcars)} columns")
```

The curly brackets might be used for something else depending on what you are trying to do.
In that case, you can use the arguments `.open` and `.close` to redefine the borders.

```{r}
n <- 1000000000 # number of children
glue("Santa uses the formula $<<n>>^{magic + love}$ to determine how much sugar to give to the elfs.",
     .open = "<<", .close = ">>")
```

There are many other use cases for glue, but I would like to highlight `glue_data()`.
This function allows you to access variables inside a given data.frame,
much the same way you can with many of the tidyverse packages.

For this example, I have created a summarized dataset.

```{r, message=FALSE}
library(dplyr)
mtcars_summarized <- mtcars %>%
  group_by(cyl) %>%
  summarise(n = n(),
            min_wt = min(wt),
            max_wt = max(wt)) %>%
  mutate_all(round, digits = 2)
```

We can then use `glue_data()` to create a little summary in text

```{r, results='hold'}
cat("`mtcars` has\n")
glue_data(mtcars_summarized,
          "{n} cars with {cyl} cylinders, with a weight range of {min_wt*1000}-{max_wt*1000} lbs")
```

This is all I have for today! 
Stay happy and I look forward to seeing you back tomorrow!

## Additional resources

- [glue 1.2.0](https://www.tidyverse.org/blog/2017/10/glue-1.2.0/)
- [Glue magic Part I](https://www.njtierney.com/post/2019/07/07/glue-magic-p1/)
- [Glue strings to data in R](https://www.youtube.com/watch?v=XQmBcpQl8K8)
