---
slug: "20"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 20: rayrender

Welcome back for the 20th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [rayrender](https://github.com/tylermorganwall/rayrender) package by [Tyler Morgan-Wall](https://twitter.com/tylermorganwall).
The **rayrender** package provides a raytracer written in R.

The package is not yet available from CRAN but can be downloaded with

```{r, eval=FALSE}
remotes::install_github("tylermorganwall/rayrender")
```

The package [website](http://www.rayrender.net/) provides many cool examples you should look at.

For this post, I'm gonna do something simple. I'll try to generate a scene with a single Christmas tree.

The data object used in this example is downloaded from [here](https://free3d.com/3d-model/christmas-tree-891764.html).

We start by generating a ground using the `generate_ground()`, this will create a specification and not render directly yet.

```{r}
library(rayrender)
generate_ground()
```

Next, we add the Christmas tree.
This is done using the `add_object()` function along with the `obj_model()` function inport the .obj file.
For this, I decide to have the tree be made of green metal.
Notice again how we just get a data.frame back with a specification.

```{r}
generate_ground() %>%
  add_object(obj_model(filename = "~/Downloads/55-ct/Christmas Tree.obj", 
                       scale_obj = 0.5,
                       material = metal(color = "green")))
```

Lastly, we pass all of that into `render_scene()` where I have changed the `lookfrom` to zoom out a little bit.

```{r}
generate_ground() %>%
  add_object(obj_model(filename = "~/Downloads/55-ct/Christmas Tree.obj", 
                       scale_obj = 0.5,
                       material = metal(color = "green"))) %>%
  render_scene(lookfrom = c(0,10,100))
```

And there we have it! A beautiful Christmas tree!

