---
slug: "22"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 22: highcharter

```{css, echo=FALSE}
tspan {
  fill: #F5F5F5;
}
```


Welcome back for the 22nd day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [highcharter](https://github.com/jbkunst/highcharter) package by [Joshua Kunst](https://twitter.com/jbkunst).

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("highcharter")
```

For the following examples, we will be using the `elf` dataset from earlier posts.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
set.seed(1234) 

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly")))
```

**highcharter** is a wrapper around the javascript library [highcharts](http://highcharts.com/) which allows you to create wonderful interactive charts.

**highcharter** lets you use a couple of different syntaxes. 
For now, I'll showcase how to use the `hchart()` function.
It has roughly the same interface as [ggplot2](https://ggplot2.tidyverse.org/).

```{r, message=FALSE}
library(highcharter)

hchart(elf, "scatter", hcaes(x = `Sugar Consumption`, y = `Jolliness`, group = Elf))
```

Clicking on the legends will disable the points on the chart. 
Try it out for yourself.

Additions to this plot are handled by piping on other functions.
Let's propose we want to change the colors, we use the ` hc_colors()` function

```{r}
hchart(elf, "scatter", hcaes(x = `Sugar Consumption`, y = `Jolliness`, group = Elf)) %>%
  hc_colors(c("#9F7234", "#DA473D", "#5AA340"))
```

```{r}
hchart(elf, "scatter", hcaes(x = `Sugar Consumption`, y = `Jolliness`, group = Elf)) %>%
  hc_colors(c("#9F7234", "#DA473D", "#5AA340")) %>%
  hc_title(text = "Buddy The Not So Jolly Elf")
```

Please check out the package [website](http://jkunst.com/highcharter/index.html) for many more examples.

<details>
 <summary>Creating `elf` dataset</summary>

```{r}
library(tidyverse)
set.seed(1234)

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly"))) %>%
  mutate_if(is.numeric, jitter)
```

</details>
