---
slug: "23"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 23: precommit


Welcome back for the 23rd day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be taking a look at the [precommit](https://github.com/lorenzwalthert/precommit) package by [Lorenz Walthert](https://twitter.com/lorenzwalthert).

The package is not yet available from CRAN but can be downloaded with the following line of code.
Also you need to have conda installed.

```{r, eval=FALSE}
remotes::install_github("lorenzwalthert/precommit")
precommit::install_precommit()
```

Once you installed what you need you just run

```{r, eval=FALSE}
precommit::use_precommit()
```

to initiate the use of [pre-commit](https://pre-commit.com/).
Now every time you run `git commit` the hooks listed in your `.pre-commit-config.yaml` will be executed before the commit.

The package website includes a section on [available hooks](https://lorenzwalthert.github.io/precommit/articles/available-hooks.html) included in the package.
This includes things like

- `readme-rmd-rendered:` Make sure README.Rmd hasn’t been edited more recently than README.md, i.e. remind you to render the .Rmd to .md before committing.

and 

- `no-browser-statement`: Guarantees you that you don’t accidentally commit code with a browser() statement in it.

Simply run `precommit::open_config()` to start configuring the hooks you want.

Lastly, I'll quote a word of warning from the [README](https://lorenzwalthert.github.io/precommit/) 
> Do not abort while hooks are running. Non-staged changes are stashed to a temp directory when the hooks are run and may not easily be recovered afterwards.
