---
slug: "3"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 3: details

Welcome back for the 3rd day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will be talking about another little nifty package called [details](https://github.com/yonicd/details) package by [Jonathan Sidi](https://twitter.com/yoniceedee).

the package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("details")
```

Suppose you want to hide some information in your html document,
while still allowing the user to see it if they want to. 
In plain html something like that would normally be done using the `details` tag.

```{r, eval=FALSE}
<details>
 <summary>Secret list of names</summary>
 Aura
 Dona
 Danyelle
 Maribel
 Evonne
 Elly
 Joye
 Monet
 Donny
 Georgeanna
</details>
```

Which would result in something like this:

```{r, echo=FALSE}
library(details)

secret <- "Aura\nDona\nDanyelle\nMaribel\nEvonne\nElly\nJoye\nMonet\nDonny\nGeorgeanna"

details(secret, "Secret list of names")
```

Putting R objects or output into a details tag used to be quite frustrating. 
Presenting **details**! 
Now all you have to do is pass (piping works too) what you want hidden into `details()`.

```{r}
library(details)
library(magrittr)

secret <- c("Madeline", "Tom", "Shavon", "Krystyna", "Callie",
            "Damon", "Shellie", "Bebe", "Candis", "Laure")

details(secret)
```

This has a few obvious use cases such as hiding session information

```{r}
sessioninfo::session_info() %>%
  details::details(summary = 'current session info')
```

and hiding spicy plots

```{r}
details(plot(sin, xlim = c(0, 20)), "my curvy plot")
```

I leave you with a little present :)

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
symbols <- c('.', '~', "'", 'O', "'", '~', '.')
layer_size <- seq(3, 45, by = 4)

things <- rep(symbols, length.out = sum(layer_size))

rows <- split(things, rep(seq_along(layer_size), times = layer_size)) %>%
  sapply(paste0, collapse = "")

details(summary = "Open for a special presents",
tibble(x = 0, 
       y = -as.numeric(names(rows)),
       labels = rows) %>%
  ggplot(aes(x, y, label = labels)) +
  geom_text(size = 10) +
  theme_void()
)
```

## Additional resources

- [Vignettes](https://yonicd.github.io/details/articles/index.html)
