---
slug: "6"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 6: skimr

Welcome back for the 6th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
When you get a new dataset it is important to do some exploratory data analysis.
One of my first tools I reach at is the [skimr](https://github.com/ropensci/skimr) package by [rOpenSci](https://twitter.com/rOpenSci). 

the package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("skimr")
```

To illustrate the package we will be using the festive dataset on [Billboard Top 100 Christmas Carol Dataset](https://www.kaggle.com/sharkbait1223/billboard-top-100-christmas-carol-dataset/data).

```{r}
billboards <- read.csv("~/Downloads/christmas_billboard_data.csv")
```

Traditionally I would have simply printed the data.frame

```{r, eval=FALSE}
billboards
```

```{r, echo=FALSE}
head(billboards)
```

used `summary()`

```{r}
summary(billboards)
```

or used the structure function `str()`

```{r}
str(billboards)
```

while they all give good information they all lack in one way or another,
and I tend to go back and forth between the different functions.
Introducing **skimr**, the main function `skim()` gives a nice overview of the data.
Complete with top-level statistics, and column statistics sorted by column type.

```{r}
library(skimr)
skim(billboards)
```

Secondly the `skim()` function returns a `skim` object that allows manipulation by **dplyr**.
Here it is simple to filter away all the variables without missing values.

```{r, message=FALSE}
library(dplyr)
skim(billboards) %>%
  filter(complete_rate < 1)
```

Hopefully, we will get to revisit this wonderfully merry dataset in the future.
