---
slug: "7"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 7: gghalves

Welcome back for the 7th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
today we will continue our look at the billboards data from [yesterday](https://www.hvitfeldt.me/pkgcal2019/6/).
The package of the day is [gghalves](https://github.com/erocoar/gghalves) created by [Frederik Tiedemann](https://github.com/erocoar).

The package is available from CRAN and can be downloaded with

```{r, eval=FALSE}
install.packages("gghalves")
```

we will be working with Santa's `elf` dataset.
The data includes 50 observations for 3 elves (150 observations total) taken monthly describing the elfly capacities.
Units have been removed due to being classified.

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
set.seed(1234) 

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly")))
```

```{r}
library(skimr)
skim(elf)
```

since we have a categorical variable (`elf`) and a couple of continuous variables we could use **ggplot2** to visualize the distributions.
Let us take a first look at the TMI (Toy Making Intensity) variable. 
We can create a boxplot for each elf by using `geom_boxplot()`

```{r}
library(ggplot2)
ggplot(elf, aes(Elf, `Toy Making Intensity`)) +
  geom_boxplot()
```

But we can't see the individual points.
you could do a second plot with `geom_dotplot()`

```{r}
ggplot(elf, aes(Elf, `Toy Making Intensity`)) +
  geom_dotplot(binaxis = "y", stackdir = "center", binwidth = 0.05)
```

But now we have two separate charts trying to show the same data.
This is where **gghalves** comes in!
**gghalves** allows you to split many of the aggregation geoms in half. 
It is easier to show with an example. 
We have the data from before and we want to showcase a boxplot and a dotplot at the same time.

```{r}
library(gghalves)
ggplot(elf, aes(Elf, `Toy Making Intensity`)) +
  geom_half_boxplot() +
  geom_half_dotplot(binwidth = 0.05)
```

by using `geom_half_boxplot()` and `geom_half_dotplot()` we we able to elegently combine 2 plot types.

The geoms respect general **ggplot2** elements so things like color

```{r}
ggplot(elf, aes(Elf, `Reindeer Training`, color = Elf)) +
  geom_half_violin() +
  geom_half_point(alpha = 0.6)
```

and factors

```{r}
ggplot(elf, aes(Elf, Jolliness, color = Elf)) +
  geom_half_violin() +
  geom_half_boxplot(side = "r") +
  facet_wrap(~ factor(`Sugar Consumption` > mean(`Sugar Consumption`), 
                      c(TRUE, FALSE), 
                      c("High Sugar Comsumption", "Low Sugar Comsumption")))
```

<details>
 <summary>Creating `elf` dataset</summary>

```{r}
library(tidyverse)
set.seed(1234)

elf <- iris %>%
  rename(Elf = Species,
         `Sugar Consumption` = Sepal.Width,
         `Toy Making Intensity` = Sepal.Length,
         `Jolliness` = Petal.Length,
         `Reindeer Training` = Petal.Width) %>%
  mutate(Elf = factor(as.numeric(Elf), labels = c("Buddy", "Twinkle", "Holly"))) %>%
  mutate_if(is.numeric, jitter)
```

</details>
