---
slug: "8"
output: 
  html_document:
    css: "calendar.css"
showonlyimage: true
description: " "
type: packagecalendar
layout:: single
---

<html>
    <link rel="stylesheet" href="calendar-post.css"/>
</html>

```{r setup, include=FALSE}
library(knitr)
library(htmltools)
opts_chunk$set(
  echo = TRUE, 
  cache = TRUE,
  collapse = TRUE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618, # 1 / phi
  out.width = "700px")
knit_hooks$set(optipng = hook_optipng)
opts_chunk$set("optipng" = "-o5")
```

```{r, echo=FALSE}
tags$section(class = "navigation",
  tags$div(class = "nav-container",
    tags$nav(
      tags$ul(class = "nav-list",
        tags$li(
          tags$a(href = "/", "Home")
        ),
        tags$li(
          tags$a(href = "/packagecalendar/2019/", "Back")
        )
      )
    )
  )
)
```

# Day 8: globe4r

Welcome back for the 8th day of the [#packagecalendar](https://twitter.com/hashtag/packagecalendar),
The package of the day is [globe4r](https://github.com/JohnCoene/globe4r) created by [John (JP) Coene](https://twitter.com/jdatap).
The **globe4r** package wraps the [globe.gl](https://github.com/vasturiano/globe.gl) library.

The package is not yet on CRAN and can be downloaded from Github with

```{r, eval=FALSE}
remotes::install_github("JohnCoene/globe4r")
```

The package is wonderfully simple. Simply start by calling `create_globe()`.
This will create a blank canvas with a globe on it.

```{r, eval=FALSE}
library(globe4r)
create_globe()
```

```{r, message=FALSE, echo=FALSE}
library(globe4r)
create_globe() %>%
  globe_background(color = "#2f3238")
```
it is interactive so you can zoom and drag as you wish.

Let's play around a little bit and load in some population data.
Population data is very important for Santa when we need to plan his route.

```{r}
data("population") # comes with globe4r
```

Let's take our globe we created with `create_globe()` and add some bars.
This is done in much the same way as in **ggplot2**.

```{r, eval=FALSE}
create_globe() %>%
  globe_bars(
    coords(lat, lon, altitude = value),
    data = population
  ) %>% 
  scale_bars_altitude(max = 0.4)
```

```{r, message=FALSE, echo=FALSE}
create_globe() %>%
  globe_bars(
    coords(lat, lon, altitude = value),
    data = population
  ) %>% 
  scale_bars_altitude(max = 0.4) %>%
  globe_background(color = "#2f3238")
```

It looks very nice! let's just give it a little more of a blueish color. 
Luckily that is the default colors for **globe4r** so we just follow in the footsteps of before to add a color aesthetic.

```{r, eval=FALSE}
create_globe() %>%
  globe_bars(
    coords(lat, lon, altitude = value, color = value),
    data = population
  ) %>% 
  scale_bars_altitude(max = 0.4) %>% 
  scale_bars_color()
```

```{r, message=FALSE, echo=FALSE}
create_globe() %>%
  globe_bars(
    coords(lat, lon, altitude = value, color = value),
    data = population
  ) %>% 
  scale_bars_altitude(max = 0.4) %>% 
  scale_bars_color() %>%
  globe_background(color = "#2f3238")
```

There are many more things you can do with **globe4r**! Please visit the [website](https://globe4r.john-coene.com/) and the original [library](https://github.com/vasturiano/globe.gl) for more inspiration.

<details>
 <summary>Setting background color</summary>

`create_globe()` will by default use a black background color.
I have secretly used `globe_background(color = "#2f3238")` to set the background color equal to the page background color.

</details>
